\vspace{-0.25em}\thetitle

### 2009-07-22 paper.tex
...

@@

The essential observation of this research is that under such representations, real flows lie near the union of a small set of low-rank subspaces.
This property allows us to perform a drastic model reduction on trace traffic patterns while preserving the essential characteristics of the original traffic.
Moreover, when observable characteristics of flows are separated from features to be predicted, this model reduction is similar to a classical linear regression:
it allows us to use a least squares optimization on observed features to predict behavior.
We use this technique to predict the following characteristics of each flow from observing only a handful of its initial packets:
\begin{enumerate}
  \item the distribution of packets sizes,
  \item the distribution of inter-packet intervals,
  \item the number of packets that will be in the flow.
\end{enumerate}
From these properties we can indirectly predict many other properties, including the total duration and data volume.

@@

>>>>

\section{Introduction}

@@

The essential observation of this research is that under such representations, real flows tend to lie near a small set of low-rank subspaces.
This property allows us to perform a drastic model reduction on trace traffic patterns while preserving the essential characteristics of the original traffic.
Moreover, when observable characteristics of flows are separated from features to be predicted, this model reduction is similar to a classical linear regression:
it allows us to use a least squares optimization on observed features to predict behavior.
We use this technique to predict the following characteristics of each flow from observing only a handful of its initial packets:
\begin{enumerate}
  \item the distribution of packets sizes,
  \item the distribution of inter-packet intervals,
  \item the number of packets that will be in the flow.
\end{enumerate}
From these properties we can indirectly predict many other properties, including the total duration and data volume.

@@

\section{Background \& Motivation}

The most fundamental tool in the investigation of linear structure in high dimensions is the singular value decomposition (\caps{SVD}).
This matrix decomposition can be applied to any real matrix and factors it into a product of three matrices:
\begin{align}
  X = US\trans{V}
\end{align}
where $U$ and $V$ are orthogonal and $S$ is diagonal, with entries of decreasing nonnegative value.
Among the useful properties of this factorization, if all but the first $k$ diagonal entries of $S$ are zeroed out, the product $US_k\trans{V}$ is the best rank-$k$ approximation of $X$ under the Frobenius matrix norm.
The rows of $US_k$ can thus be viewed as an optimal $k$-dimensional simplification of the rows of $X$ in the new coordinate system given by the columns of $V$.

\begin{figure}[!b]
\vspace{0.5em}
\begin{center}
\subfloat[IETF 60]{\includegraphics[width=1.6in]{svd/ie60}}
\subfloat[IETF 67]{\includegraphics[width=1.6in]{svd/ie67}}
\subfloat[SIGCOMM 2004]{\includegraphics[width=1.6in]{svd/sc04}}
\subfloat[UCSD]{\includegraphics[width=1.6in]{svd/ucsd}}
\caption{SVD scatter plots for various traces.} 
\fig{svd}
\end{center}
\vspace{-0.85em}
\end{figure}

% The most direct way to demonstrate the motivating insight of this research is with pictures.

\section{Methodology}

\section{Results}

\section{Discussion}

\section{Conclusions}
